HyperLogLog: Exponentially Bad in Adversarial Settings

### 2022-02-07 docs/HLL_exp_bad/main.tex
right aligning table 4 and updating URL for presto

The S2 adversary can insert items and knows the hash function $h$ and number of buckets $m$, but is otherwise blind. Such an adversary is quite realistic. For example, both the Redis and Presto implementations of HLL use a fixed hash function and parameters that can be read off from source code.\footnote{See \url{https://github.com/redis/redis/blob/unstable/src/hyperloglog.c\#L397}, \url{
https://github.com/redis/redis/blob/unstable/src/hyperloglog.c\#L467} for Redis and 
\url{https://github.com/prestodb/presto/blob/2ad67dcf000be86ebc5ff7732bbb9994c8e324a8/presto-main/src/main/java/com/facebook/presto/type/khyperloglog/KHyperLogLog.java\#L20}
for Presto.}

@@

\begin{table*}[tb!]
\begin{center}
\caption{Attack results for HLL in Redis, averaged over 50 iterations.}\label{table:tab3}
\begin{tabular}{| m{11em} | m{4em} | m{4.2em} |}
    \hline
    \textbf{Scenario} &  \multicolumn{2}{c|}{S2} \\ \hline
    %\textbf{HLL initially empty?} & no & yes \\ \hline
    \textbf{Original Card. Est.} & 0 & 139,967 \\ \hline
     \textbf{$\epsilon$} &  0.5 & - \\ \hline
    \textbf{\# Items added} & 524,210 & 524,454\\ \hline
    \textbf{Final Card. Est.} & 13,185 & 139,967 \\ \hline
\end{tabular}
\end{center}
\end{table*}
%\todo[inline]{Results from Redis or GBQ if we get them.}

>>>>

The S2 adversary can insert items and knows the hash function $h$ and number of buckets $m$, but is otherwise blind. Such an adversary is quite realistic. For example, both the Redis and Presto implementations of HLL use a fixed hash function and parameters that can be read off from source code.\footnote{See \url{https://github.com/redis/redis/blob/unstable/src/hyperloglog.c\#L397}, \url{
https://github.com/redis/redis/blob/unstable/src/hyperloglog.c\#L467} for Redis and 
\url{https://github.com/airlift/airlift/blob/master/stats/src/main/java/io/airlift/stats/cardinality/HyperLogLog.java\#L58}
for Presto.}

@@

\begin{table*}[tb!]
\begin{center}
\caption{Attack results for HLL in Redis, averaged over 50 iterations.}\label{table:tab3}
%\begin{tabular}{| m{11em} | m{4em} | m{4.2em} |}
\begin{tabular}{| c | r | r |}
    \hline
    \textbf{Scenario} &  \multicolumn{2}{c|}{S2} \\ \hline
    %\textbf{HLL initially empty?} & no & yes \\ \hline
    \textbf{Original Card. Est.} & 0 & 139,967 \\ \hline
     \textbf{$\epsilon$} &  0.5 & - \\ \hline
    \textbf{\# Items added} & 524,210 & 524,454\\ \hline
    \textbf{Final Card. Est.} & 13,185 & 139,967 \\ \hline
\end{tabular}
\end{center}
\end{table*}
%\todo[inline]{Results from Redis or GBQ if we get them.}
